\documentclass[11pt,a4paper,sans]{moderncv}        

% moderncv themes
\moderncvstyle{casual}                            
\moderncvcolor{black}                            
%\nopagenumbers{}

% adjust the page margins
\usepackage[scale=0.8]{geometry}
\setlength{\hintscolumnwidth}{2.2cm} 

% personal data
\name{Tim A.}{Pobst}
\address{7620 Alki Lane}{Knoxville TN 37919}{}
\phone[mobile]{(865)~484~6883}
\email{tim.pobst@gmail.com}
\social[linkedin][https://www.linkedin.com/pub/tim-pobst/87/60/8a]{tim-pobst}

% bibliography with mutiple entries
\usepackage{multibib}
\newcites{article}{{Peer Reviewed Articles}}
%---------------------------------------------------------------------------
%            content
%---------------------------------------------------------------------------
\begin{document}
\makecvtitle

% Education
\input{Education}

\section{Engineering Experience}

\cventry{2011-2014}{Graduate Student Researcher}{University of Tennessee}{Knoxville, TN}{}{
  \emph{Water Quality Laboratory supervised by Dr. John S. Schwartz}
	\begin{itemize}
		%\item Collected river/stream water samples and measured flow using USGS standard protocols. %Used SonTek RiverSurveyor equipment for flow measurement.
 		%\item Conducted water quality analysis in streams utilizing field instruments and laboratory equipment.% (ICP, autotitrator, wet chemistry techniques).%; analysis included pH, conductivity, TSS, anions/cations, and dissolved metals. (data sondes) 
		\item Managed a database of stream quality measurements for 43 sites in the Great Smokey Mountains National park (GRSM).
		\item Managed field operations for the GRSM, Noland Divide monitoring station: a remote study site for atmospheric pollutant deposition, soil biogeochemistry, and watershed transport.
	\end{itemize}}

\cventry{2010-2011}{Water Resources Group Leader}{University of Tennessee}{Knoxville, TN}{}{
  \emph{Senior Design Class for the Civil and Environmental Engineering Department}
 	 \begin{itemize}
	    \item Planned and designed storm water drainage system for TDOT project in Farragut, Tennessee
	    \item Estimated flow capacity for creek and US70/11 bridge crossing and culverts.
 	 \end{itemize}}

%\cventry{2009-2011}{Undergraduate Research Assistant}{University of Tennessee}{Knoxville, TN}{}{
  %\emph{Lab and Field work for Dr. John S. Schwartz's graduate students}
%\begin{itemize}
	%\item Responsibilities incuded: Equipment and lab ware washing, sub-sampling; and water quality sample collection responsibilities for GRSM and OSM.
%\end{itemize}}%, mud drying and weighing

\section{Extracurricular Experience}

\cventry{2012-}{Coach}{University of Tennessee}{Knoxville, TN}{Women's Ultimate Frisbee }{\emph{Run the practices and coach the tournaments}
	\begin{itemize}
		\item Teach strategies and techniques to all levels of experience, while analyzing strengths and weaknesses for a competitive team. 
		\item Collaborate with other players/coaches of different views and experiences to strengthen the team.
		\item Remain calm and practice patience constantly.
	\end{itemize}
}

\cventry{2006-2007}{Resident Assistant}{University of Tennessee}{Knoxville, TN}{}{\emph{Assisted 38 male freshmen}
	\begin{itemize}
		\item Fostered a community supportive to academic achievement, responsible decision making.
		\item Promoted community through planned and spontaneous social and educational programs.
		\item Mediated conflicts and educated residents about their responsibilities.
	\end{itemize}}

% Skills and Interests
\input{SkillIntrest}

\section{Honors \& Awards}
\cventry{}{Boy Scouts of America}{Troop 135}{Franklin, TN}{}{Eagle Scout}

% References
%\section{References}
%\cvitem{}{Available upon request}

\end{document}
